Checking Big Suffix and LCP Arrays by Probabilistic Methods

### 2017-02-13 draft/draft.tex
2017/02/13

	For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures and should be verified to ensure their correctness after construction. We propose in this paper two methods to probablisitically check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting function, in terms of that the checking result is wrong with only a negligible probability. The first method checks the lexical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs. The second method first applies the fingerprinting technique to check a subset of the given suffix and LCP arrays, then it produces the whole arrays from the verified parts following the induced-sorting principle and compares the induced and input copies with each other for verification.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Suffix and LCP arrays, verification, Karp-Rabin fingerprinting function.
\end{IEEEkeywords}}

@@

Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly. In dozens of applications, these two data structures are combined to constitute a powerful full-text index for massive data, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity. During the past decades, much effort has been put on the development of designing efficient suffix array construction algorithms~(SACAs). Specifically, the first internal-memory algorithm for building SA was introduced in~\cite{Manber1993}. From then on, a plethora of SACAs have been proposed on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}. In respect of the design on LCP-array construction algorithms~(LACAs), the existing works can be classified into two categories, where the algorithms of the first category compute the suffix and LCP arrays in the same time~\cite{Fischer11, Bingmann12, Flick2015} and that of the second category take the suffix array (SA) and/or Burrows-Wheeler transform (BWT) as input to facilitate the computation~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013, Karkkainen2016}.

While the study for efficient construction of suffix and LCP arrays is evolving, the programs implementing the proposed algorithms are commonly provided ``as is", with the purpose only for the performance evaluation experiemnts of the articles where they are reported. That is, these programms give no guarantee that they have correctly implemented the proposed algorithms. The programs for recently proprosed algorithms are becoming much more complicated than before, casuing more difficulties for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}. As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array. For example, such a checker is provided in the software packages (like SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and DC3~\cite{Dementiev08}) for constructing suffix and/or LCP arrays. In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~\cite{Bille2013}. In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.

@@

In this article, we propose two methods for probablistically checking the give suffix and LCP arrays in external memory using a fingerprinting techinque. As observed from the experimental results, our program for the algorithm designed on Method A outperforms that for the algorithm designed on Method B in both running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in time and I/O performance.

@@

>>>>

For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures, and there are at least two needs in practice for checking their correctness, i.e. program debugging and verifying the arrays constructed by probabilistic algorithms.
We propose in this paper two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability. Our first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs. This approach is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given one for verification.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Suffix and LCP arrays verification, Karp-Rabin fingerprinting technique, external memory.
\end{IEEEkeywords}}

@@

Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly. Particularly, these two data structures constitute the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity. The first algorithm for building SA in internal memory was presented in~\cite{Manber1993}. From then on, much effort has been put on the development of designing efficient SA construction algorithms~(SACAs) on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}. In respect of the design on LCP-array construction algorithms~(LACAs), the existing works can be classified into two categories, where the algorithms of the first category compute the suffix and LCP arrays in the same time~\cite{Fischer11, Bingmann12, Flick2015} and that of the second category take the suffix array (SA) and/or Burrows-Wheeler transform (BWT) as input to facilitate the computation~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013, Karkkainen2016}. Currently, the fastest algorithms of linear time and space complexity are based on induced sorting principle. However, some sub-linear algorithms reported recently achieved a better performance by exploiting the full use of computation resource in a multi-core environment.

{\color{red} There are at least two needs in practice for checking the correctness of a suffix or LCP array, i.e. program debugging and verifying the array constructed by a probabilistic algorithm.}
While the study for efficient construction of suffix and LCP arrays is evolving, the programs implementing the proposed algorithms are commonly provided ``as is", with the purpose only for the performance evaluation experiemnts of the articles where they are reported. That is, these programms give no guarantee that they have correctly implemented the proposed algorithms. The programs for recently proprosed algorithms are becoming much more complicated than before, casuing {\color{red} challenges} for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}. As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array. For example, such a checker is provided in the software packages (like SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and DC3~\cite{Dementiev08}) for constructing suffix and/or LCP arrays. In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~\cite{Bille2013}. In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.

@@

In this article, we propose two methods for probablistically checking the give suffix and LCP arrays using external memory. According to the experimental results, our program for Method A has a better performance than that for Method B with respect to the running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in the time and I/O effciency. We think these two methods could potentially be a xxxx .

@@

We are intended for ....

put emphasis on

with the same ease as when

The biggest difference between two is that ...

Toward the end, ...

they are designed to be both easy to interpret on ... and easily traslated into ... (they are designed to be easily implemented in classic external memory models)

Having a ... eliminates .... (random accesses), access ordering

Not only are ..., but

The fingerprints are calculated on the fly during the scan of x ...

become so good that they are competitive with ...., and in some cases, even outperform them ...

concurrent programming is needed to make sure ....

designed to adapt to an evolving environment

most importantly

exchanges data between the computer presenting the applet and the computer serving it.

carries out sophisticated calculations

Presumably because

make ... capable of ...

greatly improve ... , it was still rather limited, though.

additional performance improvements

close the chapter with ...

gain

which pose ...

integrate with

In this chapter, we will ... how to ... and how to ...

we prefer the comfort of an integrated development environment, ( prefer the low cost of fingerprinting techinques)

space-hungry

begin exploring ... by ...

commnuicate the monmentous advances

extremely simple

check each number is present in the suffix array.

go into much more greater details

stand-alone algorithms for computing suffix arrays only and has been reused to

invoke/call

the mechanics of ...

If you have done sth, then when you do sth, you end up with ...

depend on the machine on which you will be running the java code ...

alleviate

The second method is invented to overcome the drawback of

in place of

as to/about

as far as

assign to a variable

stated goals

intermediate steps

tied to the behavior of

an assortment of

following the footsteps of

characters in the input string are processed from left to right

in greater detail
